Fuzzy joins through deep learning

### 2018-07-29 paper2018/introduction.tex
minor change in flow

Merging two datasets (the so-called join operation) is a key operation in data management.  Data management systems have largely focussed solely on equi-joins, where equality of strings or numeric values of the two columns determines if rows should be joined.  However, equality at a string level is inadequate because the same entity may in many cases be expressed with slight variations of the same name, as shown in Table~\ref{table-example} (e.g., \textit{Douglas Adams} and \textit{Douglas Noel Adams}).  This problem occurs for many entity types such as company names, addresses, product descriptions, and conference venues.

@@

In this paper, we propose a novel data driven approach to the problem of joining different representations of the same entity.  Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.  Because a deep learning model can learn the features necessary for matching from the data, it should in theory be able to generalize better to new datasets than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.   Conceptually, our approach is similar in spirit to the approach described in \cite{auto-join-joining-tables-leveraging-transformations}, but we use deep neural networks to learn the right function for the join operation instead of synthesizing different programs for different entity types.  The advantage of building such a function over the approach described in \cite{auto-join-joining-tables-leveraging-transformations} is that we can use this function in novel ways to completely eliminate the blocking step that is typically needed to identify the set of potentially joinable rows, as we describe below.

Our solution to the join problem involves building a system that performs deep metric learning.  That is, the specific function the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.  This is typically achieved by training a so-called `triplet siamese network'.  At training, the network is given a triplet consisting of an `anchor' (e.g. \textit{Douglas Adams}), a positive element (e.g. \textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair (above some margin $m$). A classification form of this function that simply learns whether two names belong to the same entity can be used to perform fuzzy joins, but then we would need a blocking strategy analogous to what has been used in the literature to identify the set of joinable pairs \cite{auto-join-joining-tables-leveraging-transformations}.

>>>>

Merging two datasets using joins is a key operation in data management.  Data management systems have largely focussed solely on equi-joins, where equality of strings or numeric values of the two columns determines if rows should be joined.  However, equality at a string level is inadequate because the same entity may in many cases be expressed with slight variations of the same name, as shown in Table~\ref{table-example} (e.g., \textit{Douglas Adams} and \textit{Douglas Noel Adams}).  This problem occurs for many entity types such as company names, addresses, product descriptions, and conference venues.

@@

In this paper, we propose a novel data driven approach to the problem of joining different representations of the same entity.  Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.  For the closely related problem of face recognition and person re-identification, deep learning networks have been used successfully to discriminate pairs that represent the same entity from those that don't.  However, we know of no work that has adapted these techniques to the problem of fuzzy joins for entity names.

Because a deep learning model can learn the features necessary for matching from the data, it should in theory be able to generalize better to new datasets than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.   Conceptually, our approach is similar in spirit to the approach described in \cite{auto-join-joining-tables-leveraging-transformations}, but we use deep neural networks to learn the right function for the join operation instead of synthesizing different programs for different entity types.  The advantage of building such a function over the approach described in \cite{auto-join-joining-tables-leveraging-transformations} is that we can use this function in novel ways to completely eliminate the blocking step that is typically needed to identify the set of potentially joinable rows, as we describe below.

Our solution to the join problem involves building a system that performs deep metric learning.  That is, the specific function the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.  As in face recognition, we do this by training a `triplet siamese network'.  However, entity names have very different properties from faces, so we needed to adapt the approaches used in face recognition to the entity matching problem with a novel method to choose the sample for training, and novel loss functions as objectives for the metric learning problem.

At training, the network is given a triplet consisting of an `anchor' (e.g. \textit{Douglas Adams}), a positive element (e.g. \textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair, using an objective function. A classification form of this function that simply learns whether two names belong to the same entity can be used to perform fuzzy joins, but then we would need a blocking strategy analogous to what has been used in the literature to identify the set of joinable pairs \cite{auto-join-joining-tables-leveraging-transformations}.
